\documentclass[a4, 12pt]{article}
\usepackage[top=0cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{setspace}
\usepackage{mdwlist}
\usepackage{titlesec}
\titlespacing*{\subsection}
{0pt}{1em}{.5em}

%opening
\title{Questionnaire Design Activity\vspace{-2em}}
\author{}
\date{}

\begin{document}

\maketitle

\noindent The purpose of this activity is to think about how to write good questions on surveys. The focus here is on measuring evaluative questions (i.e., those about a respondent's opinions, attitudes, values, etc.). Each item below is a concept that we might want to operationalize in a survey questionnaire. For each item, generate two (2) possible ways of measuring this concept. Then, weigh the advantages and disadvantages of each approach. For example, you might want to consider any of the following features:

\begin{itemize*}
	\item Is the question easy for respondents to understand? Might the question (or the answer options) require clarification after being read?
	\item Are the number and types of response options appropriate? Are the categories sufficiently distinct from one another?
	\item Is a ``no opinion,'' ``don't know,'' or ``neither support nor oppose'' response option available?
	\item Is one survey item (i.e., one question) sufficient to measure this construct?
	\item How long does it take to read and answer this question?
\end{itemize*}


\subsection*{Concepts}

\onehalfspacing

\begin{enumerate*}
	
\item Example: Support for the current Danish government.

\subsection*{Set A}

\item Opinion about mass transportation provision in Aarhus municipality.

\item Opinion about one's workplace supervisor.

\subsection*{Set B}

\item Opinion toward the European Union.

\item Opinion about quality of education at Aarhus University.

\subsection*{Set C}

\item Opinion toward Danish immigration policy.

\item Opinion about quality of social life in Aarhus.

\subsection*{Set D}

\item Opinion toward the major political parties in Denmark.

\item Opinion about one's current mobile phone company.

\subsection*{Set E}

\item Opinion about preferred level of spending on welfare provision.

\item Opinion about one's last meal purchased at a restaurant.
	
\end{enumerate*}

\end{document}
