\documentclass[12pt, a4]{article}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{setspace}
\usepackage{mdwlist}
\usepackage{titlesec}

\title{Questionnaire Design Activity\vspace{-2em}}
\author{}
\date{}

\begin{document}

\maketitle

\noindent The purpose of this activity is to practice writing questions, organizing questions into a complete survey instrument, and working collaboratively on survey development. Your task is to develop a complete questionnaire for a survey that you will administer to student respondents at Aarhus University. You will work in teams and each time must develop an overall research topic for their survey, determine the set of constructs they want to measure in the survey, draft each survey item (including an introduction to the survey), and prepare an organized draft of the entire survey instrument to share with the class.

\section{Requirements}
There are several requirements for the survey:
\begin{enumerate}
    \item The survey must be written entirely in English.
    \item The survey will be administered to Aarhus University students, so should be appropriate for this population.
    \item The survey must help to test one or more research questions.
    \item The survey must include the following:
        \begin{itemize}
            \item An introduction describing the purpose of the survey
            \item At least 15 survey questions
            \item At least three evaluative-type questions
            \item At least three recall-type questions
            \item At least one potentially sensitive question
            \item At least one set of items involving potential context or question-order issues
        \end{itemize}
\end{enumerate}

\section{Requirements}
You must work coherently as a team to plan, write, and organize your questionnaire. You will present your questionnaire to the class in the form of slides. Your slides must describe your research question, an overview of the survey (outlining what you are asking and in what order), a discussion of survey mode and an estimate of the duration of the survey interview, and all of the complete survey items (probably one item per slide). The presentations must be ready by minutes before the end of today's class time.

\end{document}
