\documentclass[12pt, a4]{article}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{setspace}
\usepackage{mdwlist}

\title{Focus Group Activity\vspace{-2em}}
\author{}
\date{}

\begin{document}

\maketitle

\onehalfspacing

\noindent The purpose of this activity is to gain experience using focus groups as a technique for preparing and evaluating a survey instrument. We will focus in this activity on using focus groups to develop questionnaires. Several individuals will be selected to lead practice focus groups, the participants for which will consist of other class members. One person in each group should be a designated note-taker, who records the important points raised in the discussion and can report back to the class on the discussions.

\section*{Plan for the Activity}

The activity will focus on a planned survey about transportation in Region Midtjylland (the region that includes Aarhus municipality). The goal of the focus group is to identify topics that should be covered on the survey and to make sure that concerns deemed important by focus group participants are adequately reflected in the question topics and response categories that will be available in the final survey instruments.

The focus group should roughly follow the structure outlined below, but can cover additional areas as deemed appropriate by the moderator. It is important that the conversation stay positive, welcoming all viewpoints, while also making sure there is a space to hear criticisms.

\begin{enumerate*}
	\item \textbf{Introduction}: The moderator should introduce the topic of the focus group to the participants
	\item \textbf{Brainstorm}: The moderator should lead the group in a constructive discussion of the modes of transportation used by group participants (e.g., bus, car, train, cycle, walking, etc.)
	\item \textbf{Decision making}: How do group members decide about modes of transportation to use? What considerations come to mind (e.g., cost, schedules, routes, etc.)?
	\item \textbf{Positives}: What do participants like about transportation in Midtjylland?
	\item \textbf{Wishes}: What do participants wish was different about transportation in Midtjylland?
	\item \textbf{Miscellany}: What hasn't been discussed so far that is important, useful, or interesting for us to include?
	\item \textbf{Survey}: What would convince you to participate in a survey about transportation in Midtjylland? What would prevent you from participating?
\end{enumerate*}

\noindent After the focus group, the moderator would normally work with the notetaker to synthesize the results. Today, the entire group should work together to use the focus group results to set a plan for the survey based on what they discussed.





\end{document}
