\documentclass[a4, 12pt]{article}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{setspace}
\usepackage{mdwlist}
\usepackage{titlesec}
\titlespacing*{\subsection}
{0pt}{1em}{.5em}

%opening
\title{Sensitive Question Activity I (B)\vspace{-2em}}
\author{}
\date{}

\begin{document}

\maketitle

\noindent The purpose of this activity is to think about sensitive topics on surveys. This activity will help you to consider how respondents experience sensitive topics.

\section*{Partner Activity}

\noindent You are going to play the role of interviewer and respondent to experience firsthand how potentially sensitive questions work in a face-to-face survey interview. \textbf{Importantly: Do NOT answer the questions.} For each question, write down how you felt as the interviewer asking the question or how you felt as the respondent in attempting to answer the question. Your partner has a different version of the questionnaire than you. Take turns in each role.

\subsection*{Interviewer Questions}

\begin{enumerate}
	%\item Which party did you vote for in the last election for the European Parliament?
	\item A lot of people are unable to get out and vote for many reasons. Did you happen to vote in the last election for the European Parliament?
	
	%\item Do you agree or disagree that it is morally wrong to gamble?
	\item Regardless of whether or not you think it should be legal, please tell me whether you personally believe that in general it is morally acceptable or morally wrong for married men and women to have an affair?
		
	%\item To the nearest 5,000kr (or 1,000 Euro), what is your parents' total household income?
	\item How does your current monthly household income compare to what it was twelve months ago? Would you say it is significantly higher now, about the same versus twelve months ago, or significantly lower now?
	
	%\item During the past 30 days, on how many days did you have at least one drink of alcohol?
	\item Have you ever stolen anything from a current or former employer?
	
	%\item To what extent do you agree with the following statement? ``Men and women should have different roles to play in society.''
	\item To what extent do you agree with the following statement? ``One of the worst things a person could do is hurt a defenseless animal.''

	%\item When was the last time you had unprotected sex?
	\item There are several diseases or infections that can be transmitted during sex. At any point in time, have you ever been told by a doctor that you had a sexually transmitted disease?
	
	%\item During today's class session, how much time have you spent on your computer on things unrelated to class?
	\item During your time in university, have you ever cheated on an exam?

\end{enumerate}


\pagebreak

\section*{Individual Activity}

\noindent Please read the following questions as if you were completing the survey for real. You do NOT need to record your answers. Instead, write down what goes through your mind as you answer each question. We will discuss those feelings and reactions in general terms after you are finished.

\begin{itemize*}\itemsep1.5em
	\item Do you believe in God?
	%\item Which comes closest to your view? ``The Bible is the word of God'' or ``The Bible is a book written by men and is not the word of God''?
	\item When you were a child, were you raised by both of your parents in the same household, by both parents about equally but in different households, raised mainly by your mother, raised mainly by your father, or were you raised by someone else?
	\item Thinking of your current relationship with your spouse or partner (or, if you are not currently in a relationship, a past spouse/partner), have you ever become so angry that one of you lost control and either yelled, broke things or tried to hurt your partner?
	\item If your spouse or romantic partner made more money than you, would it threaten the relationship?
	\item If you had a child who told you he or she was gay or lesbian, would you be very upset, somewhat upset, not very upset, or not upset at all?
	\item Within the last twelve months, have you or any member of your household been sexually assaulted or raped?
	\item Thinking about the time since your 18th birthday, have you ever had sex with a person you paid or who paid you for sex?
	%\item How serious a problem do you think the issue of immigration is for the country right now: very serious, somewhat serious, not too serious, or not at all serious?
	\item How often do you feel you have to lie or cheat? Often, occasionally, rarely, or never?
	\item Do you favor or oppose making it more difficult to access pornography on the Internet?
	%\item Would you say you are for or against allowing child pornography because it's a from of free speech?
	\item In the dispute between Israel and the Palestinians, how much do you sympathize with the Palestinians? A lot, some, not much, or not at all?
	\item Just your impression, in Europe today, is there a lot of discrimination against Muslims, or not?
	\item If marijuana were legalized for recreational use in Denmark, would you definitely use it, probably use it, probably not use it, or definitely not use it?
	\item Overall, how well would you say your mental or emotional health needs are being met today? Very well, somewhat well, not too well, or not at all well?
\end{itemize*}


\end{document}
