\documentclass[compress, 12pt]{beamer} %Makes presentation

\input{preamble}

\title{Questionnaire Design II}

\date[]{October 6, 2014}

\begin{document}

\frame{\titlepage}

\frame{\tableofcontents}

\section{Construct Validity}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Construct Validity}
	\begin{itemize}\itemsep2em
		\item Definition?
		\item<2-> How do we know if a survey response is ``true''?
	\end{itemize}
}

\frame{
	\frametitle{Validation studies}
	\begin{enumerate}\itemsep2em
		\item Some survey responses can be \textit{validated}
		\item Easy for some behavioral constructs
		\item Direct observation, registry data, etc.
	\end{enumerate}
}

\frame{\frametitle{Questions about construct validity?}}

\section{Recall-type Questions}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Recall-type Questions}
	\begin{itemize}\itemsep2em
		\item Knowledge
		\item Behavior
		\item Events
	\end{itemize}
}


\frame{
	\frametitle{Recalling Knowledge}
	\begin{itemize}\itemsep2em
		\item Factual items with ``true'' responses
		\item Examples
		    \begin{itemize}
		        \item Political knowledge
		        \item Knowledge about products/services
		        \item General knowledge
		    \end{itemize}
		\item Knowledge varies widely across individuals
	\end{itemize}
}

\frame{
	\frametitle{Recalling Knowledge}
	\begin{itemize}\itemsep2em
		\item How do we deal with ``don't know'' responses?
		    \begin{itemize}
		        \item Genuine expression of lack of knowledge?
		        \item Insufficient time to think?
		        \item Question was unclear/ambiguous?
		    \end{itemize}
		\item<2-> Huge debate about this
	\end{itemize}
}



\frame{
	\frametitle{Recalling Behaviors}
	\begin{itemize}\itemsep2em
		\item Things respondent did in the past
		\item Examples
            \begin{itemize}
                \item Media use
                \item Eating/dietary habits
                \item Past voting
            \end{itemize}
        \item Challenging to measure accurately
        \item Can be easily validated
	\end{itemize}
}

\frame{
	\frametitle{Measuring Behaviors}
	\begin{itemize}\itemsep2em
		\item Provide counts for a given \textit{reference period}
        \item Provide a rate within a reference period
		\item List specific behavioral events
		    \begin{itemize}
    		    \item Allows follow-up questioning
		    \end{itemize}
	\end{itemize}
}


\frame{
	\frametitle{Recalling Events}
	\begin{itemize}\itemsep2em
		\item Things that happened as specific points in time
		\item Examples
            \begin{itemize}
                \item Events in the news
                \item Crime victimization
                \item Time when you felt angry
            \end{itemize}
		\item Same problems as with other types of recall
	\end{itemize}
}

\frame{
	\frametitle{What affects responses to recall questions?}
	\begin{itemize}\itemsep1em
        \item Question misunderstanding
            \begin{itemize}
                \item Vague concepts
                \item Confusing or long wording
            \end{itemize}
        \item<2-> Forgetting
        \item<3-> Recency/primacy biases among responses
        \item<4-> Motivated misreporting
        \item<5-> Reference period ambiguity
        \item<6-> Rare events
        \item<7-> True ``don't know'' responses
	\end{itemize}
}


\frame{
	\frametitle{Motivated misreporting}
	\begin{itemize}\itemsep2em
        \item Intentionally giving an incorrect response
            \begin{itemize}
                \item Applies to recall and evaluative questions
            \end{itemize}
        \item<2-> Examples?
        \item<3-> Several common biases
            \begin{itemize}
                \item<3-> Social desirability bias
                \item<3-> Positivity bias
                \item<3-> Acquiescence bias
                \item<3-> Demand characteristics
            \end{itemize}
	\end{itemize}
}


\frame{\frametitle{Questions about recall questions?}}

\section{Sensitive Topics}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Sensitive Questions}
	\begin{itemize}\itemsep2em
		\item Definition: Topics ``seen as intrusive or embarrassing''
		\item Examples?
		\item<2-> Factors affecting topic sensitivity
		    \begin{itemize}
                \item<2-> Individual differences
    		    \item<2-> Mode
    		    \item<2-> Interviewer
    		    \item<2-> Survey context
    		    \item<2-> Survey sponsorship
    		    \item<2-> Perceived privacy
		    \end{itemize}
		\item<3-> Why do we care?
	\end{itemize}
}

\frame{
	\frametitle{Activity: Answering Sensitive Questions}
	\begin{enumerate}\itemsep2em
		\item Pair Activity
		    \begin{itemize}
    		    \item ``Role play'' interviewer and respondent
    		    \item Do NOT answer the questions
    		    \item Record your thoughts/feelings/reactions to each question
		    \end{itemize}
		\item Individual Activity
		    \begin{itemize}
    		    \item Complete questionnaire on your own
    		    \item Do NOT answer the questions
    		    \item Record your thoughts/feelings/reactions to each question
		    \end{itemize}
		\item Then we will discuss together
	\end{enumerate}
}

\frame{\frametitle{Questions about sensitive topics?}}

\frame{
	\frametitle{Eliciting Answers to Sensitive Questions}
	\begin{itemize}\itemsep2em
		\item Ensure privacy, anonymity, or confidentiality
		\item Change modes
		\item Indirect measures
		    \begin{itemize}
    		    \item ``List experiment''
		    \end{itemize}
		\item Provide population rates
		\item Placement in survey instrument
	\end{itemize}
}


\frame{
	\frametitle{Activity: Writing Sensitive Questions}
	\begin{enumerate}\itemsep2em
		\item Work in groups
		\item Select a potentially sensitive topic
		\item Write 2--3 survey questions on that topic
		\item Present to the class how your approach eases sensitivity
	\end{enumerate}
}

\section{Preview of Next Time}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Agenda for next class}
	\begin{itemize}\itemsep1em
		\item \textbf{No meeting next week (Week 42)}
		\item Mode of interview
		\item Budgets
		\item Mode comparisons
	\end{itemize}
}

\frame{
	\frametitle{Assignment for next week}
	\begin{itemize}\itemsep1em
		\item Draft of your questionnaire!
        \item With remaining time:
            \begin{itemize}
            \item Discuss this week's assignment
            \item Discuss strategies for question writing
            \end{itemize}
	\end{itemize}
}


\appendix
\frame{}

\end{document}
