\documentclass[compress, 12pt]{beamer} %Makes presentation

\input{preamble}

\title{Who is being surveyed?}

\date[]{September 15, 2014}

\begin{document}

\frame{\titlepage}

\frame{\tableofcontents}

\section{Assignment}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Assignment for this week}
	\begin{enumerate}\itemsep1em
		\item Form groups of 3 (or so)
		\item Discuss the surveys you identified online
		\item Select one of those from your group to present to the class
		\item Think about: coverage, representativeness, sample size
	\end{enumerate}
}


\section{Review of Last Week}
\frame{\tableofcontents[currentsection]}

\frame<1-4>[label=lastweek]{
	\frametitle{Ideas from last week}
	\begin{enumerate}\itemsep1em
		\item<1-> What is a population?
		\item<2-> What is a sampling frame?
		\item<3-> What is a sample?
		\item<4-> How do we construct a sampling frame? % then do sampling frame activity
		\item<5-> What is the process of determining necessary sample size for a study?
	\end{enumerate}
}

\frame{
	\frametitle{Activity!}
	\begin{itemize}\itemsep2em
		\item Work in pairs
		\item Develop two sampling frames/sampling strategies for a population
		\item Share with class and discuss
	\end{itemize}
}


\againframe<4-5>{lastweek}

\section{New Material to Cover}
\frame{\tableofcontents[currentsection]}

\subsection{Readings}
\frame{\tableofcontents[currentsubsection]}

\subsection{Total Survey Error}
\frame{\tableofcontents[currentsubsection]}

\frame{
	\frametitle{Total Survey Error}
	\begin{itemize}\itemsep2em
	\item What sources of survey error have we discussed so far?
	\item<2-> Now we also think about sampling error
	\end{itemize}
}


\frame{
	\frametitle{Sampling Error}
	\begin{itemize}\itemsep2em
		\item Definition?
		\item<2-> Unavoidable!
		\item<3-> Sources of sampling error:
			\begin{itemize}
				\item Sampling
				\item Sample size
				\item Unequal probabilities of selection
				\item Non-Stratification
				\item Cluster sampling
			\end{itemize}
	\end{itemize}
}



\frame{
	\frametitle{Readings for this week}
	\begin{enumerate}\itemsep1em
		\item<1-> Walter and Enticott
		\item<2-> Reinisch et al.
		\item<3-> AAPOR Report
	\end{enumerate}
}



\subsection{Online Panels}
\frame{\tableofcontents[currentsubsection]}

\frame{
	\frametitle{Advantages and Disadvantages}
	\begin{itemize}\itemsep2em
	\end{itemize}
}


\subsection{Stratified Sampling}
\frame{\tableofcontents[currentsubsection]}

\frame{
	\frametitle{Simple Random Sampling (SRS)}
	\begin{itemize}\itemsep2em
		\item Advantages
			\begin{itemize}
				\item Simplicity of sampling
				\item Simplicity of analysis
			\end{itemize}
		\item Disadvantages
			\begin{itemize}
				\item Need sampling frame and units without any structure
				\item Possibly expensive
			\end{itemize}
	\end{itemize}
}


\frame{
	\frametitle{Important considerations}
	\begin{itemize}\itemsep1em
		\item 
	\end{itemize}
}




\section{Preview of Next Week}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Assignment for next week: Task}
	\begin{itemize}\itemsep1em
		\item What is your research topic/question?
		\item What is your population?
		\item What is your sampling frame? How does it over-cover or under-cover your population?
		\item How do you plan to sample?
		\item How big of a sample do you need?
	\end{itemize}
}

\frame{
	\frametitle{Assignment for next week: Procedure}
	\begin{itemize}\itemsep1em
		\item Present it in-class next week
		\item Email me your assignment (by Saturday night)
		\item Meet with me tomorrow or Wednesday
	\end{itemize}
}

\frame{
	\frametitle{Next week's agenda}
	\begin{itemize}\itemsep1em
		\item Cluster sampling
		\item Concept definition and operationalization
		\item Opinion questions and factual questions
		\item Practice developing questions
	\end{itemize}
}


\appendix
\frame{}

\end{document}
