\documentclass[12pt]{beamer} %Makes presentation

\input{preamble}

\title{What can surveys tell us?}

\date[]{September 8, 2014}

\begin{document}

\frame{\titlepage}

\frame{\tableofcontents}

\section{Basic procedural details}
\frame{\tableofcontents[currentsection]}

\frame{
\frametitle{Basic procedural stuff}	
	\begin{itemize}\itemsep1em
		\item Syllabus, slides, etc. are online:\\
		\href{http://www.thomasleeper.com/surveycourse}{http://www.thomasleeper.com/surveycourse}
		\item When should we take breaks?
		\item<2-> Proposal: 11:15--12:00, 12:30--13:15, 13:20--14:00
	\end{itemize}
	
}

\section{First assignment}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Introduce us to you}
	\begin{itemize}\itemsep1em
		\item What is your name?
		\item Where are you from?
		\item What do you plan to do after AU?
	\end{itemize}
}

\frame{
	\frametitle{Form groups and discuss}
	\begin{itemize}\itemsep1em
		\item Share your assignment
		\vspace{1em}
		\item What things are common between your experiences?
		\item What lessons do you take away from your experience as a research participant?
	\end{itemize}
		
}


\section{Course Overview}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Course Objectives}
	\footnotesize
	\begin{enumerate}\itemsep0.5em
		\item Identify and analyze the usefulness of survey methods for conducting research and evaluating programs, policies, and outcomes
		\item Identify sources of error and bias in surveys
		\item Explain how sampling procedures enable estimation of population parameters and evaluate the implications of differences in sampling techniques
		\item Demonstrate how to successfully manage large survey data collection efforts
		\item Evaluate the quality of surveys in terms of sampling, interviewing procedures, and questionnaire content 
		\item Apply methodological and substantive knowledge from the course to the design and implementation of an original survey
	\end{enumerate}
}


\frame{
	\frametitle{Exam}
	\begin{itemize}\itemsep1em
		\item Home assignment
		\item 6,000 words
        \begin{itemize}
        \item Longer if you work collaboratively
        \end{itemize}
		\item Design and pilot test an original survey
		\item Present a draft during last two weeks of class
	\end{itemize}
}

\frame{
	\frametitle{Weekly Activities}
	\begin{itemize}\itemsep1em
		\item Reading before class
		\item Short writing assignments due each class
		\item Mix of discussion, activities, and lecture
	\end{itemize}
}

\frame{
	\frametitle{Outline}
	\begin{itemize}\itemsep1em
		\item Surveys, Populations, Sampling (3 weeks)
		\item Questionnaire design (4 weeks)
		\item Pilot testing (3 weeks)
		\item Data management (2 weeks)
		\item Presentations (1--2 weeks)
	\end{itemize}
}


\section{Introduction to Surveys}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{What is a survey?}
}


\frame{
	\frametitle{Why do we do surveys?}
}


\frame{
	\frametitle{Research designs}
	\begin{itemize}\itemsep2em
		\item Prevalence
		\item Changes
		\item Causal Effects
	\end{itemize}
}

\frame{
	\frametitle{``Think--Pair--Share'' Activity}
	\begin{itemize}\itemsep1em
		\item Take handout
		\item Read each abstract
		\item Figure out: How does a survey help the authors answer their research question?
	\end{itemize}
}

\section{Preview of Next Week}
\frame{\tableofcontents[currentsection]}

\frame{
	\frametitle{Next week's agenda}
	\begin{itemize}\itemsep1em
		\item Populations and sampling frames
		\item Simple random sampling
		\item Convenience sampling
		\item Discuss your proposed research topics
	\end{itemize}
}

\frame{
	\frametitle{Final activity}
	\begin{itemize}\itemsep1em
		\item<1-> Generate three possible research topics/questions
		\item<2-> Discuss in small groups
		\item<3-> Homework: Write up one question in detail
	\end{itemize}
}


\appendix
\frame{}

\end{document}
